Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-04-20 main.tex
Adding new lines about usage of SOM in astronomy
Updates from ShareLaTeX
adding props_vs_props plot and writing about it. Add more comparison with T12

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand{\sii}{S~{\textsc II}\ } 
\newcommand{\oiii}{O~{\textsc III}\ } 
\newcommand{\hi}{H~{\textsc I}\ }

@@

\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: data mining approach}
\author{rahmani.sahar }
\date{\today}
\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
\maketitle

@@

\import{sections0.0/}{method0.0.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{sections0.0/}{results0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Discussion
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

@@

4) ...
\section*{ACKNOWLEDGMENTS}
S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining_h.bib}

>>>>

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \halpha    {H$\alpha $\ }
\newcommand \um    {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand{\sii}{S~{\textsc II}\ } 
\newcommand{\oiii}{O~{\textsc III}\ } 
\newcommand{\hi}{H~{\textsc I}\ }

@@

\title[SOM: classifying high $Z$ galaxies]{Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach}
\author{rahmani.sahar }
\date{\today}
\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{2}$, P.~Barmby$^{1}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
\maketitle

@@

\import{sections0.01/}{method0.01.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Results
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{sections0.01/}{results0.01.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Discussion
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

@@

4) We plot the properties of the galaxies using new classification and see the correlation between age and SSFR and stellar mass of the galaxies.

\section*{ACKNOWLEDGMENTS}
S.R. and P.B. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining_h.bib}

### 2016-04-20 sections0.0/data0.0.tex
adding props_vs_props plot and writing about it. Add more comparison with T12

\section{DATA}
\label{sec: data}
%Basically these are 2012 data
As mentioned in Sec.~\ref{sec: intro}, for training neural networks, we used SED templates from K96.
Moreover, to test our networks, we obtained SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
 \subsection{Kinney spectral model}
    K96 produced a template of UV-optical spectra of 70 star forming and quiescent galaxies which can be used to classify the SED of the high redshift galaxies.
    They introduced 12 types of spectra based on their morphological type or colour excess for quiescent and star burst galaxies, respectively (~\ref{fig: k96}).
    %I know it is exactly as Hossein's plot, but I can see any other choice to put here.
    \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{../images/k96.jpg}
        \caption{K96 spectra template for 12 types of galaxies.Type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belongs to early type galaxies. Star burst galaxies spectra are indicated with SB 1 to 6. Higher numbers represents more inartistic colour extinction.}
        \label{fig: k96}
    \end{figure}
    The quiescent group of galaxies includes Elliptical (E), Bulge (B), S0, Sa, Sb, and Sc galaxies.
    Bulge groups represents galaxies similar to M31 and M81, which their UV and optical spectroscopy dominated by the stellar population in their bulges.

>>>>

\section{DATA}
\label{sec: data}
%Basically these are 2012 data
As mentioned in Sec.~\ref{sec: intro}, for training neural networks, we used SED templates from K96.
Moreover, to test our networks, we obtained SED and physical properties of 142 galaxies at 0.5 < $z$ < 1 from T12.
 \subsection{Kinney spectral model}
     \begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{../images/k96.jpg}
        \caption{K96 spectra template for 12 types of galaxies from T12 paper.Type of each template is shown in each frame. Plots B, E, S0, Sa, Sb and SC show spectra that belongs to early type galaxies. Star burst galaxies spectra are indicated with SB 1 to 6. Higher numbers represents more inartistic colour extinction.}
        \label{fig: k96}
    \end{figure}
    K96 produced a template of UV-optical spectra of 70 star forming and quiescent galaxies which can be used to classify the SED of the high redshift galaxies.
    They introduced 12 types of spectra based on their morphological type or colour excess for quiescent and star burst galaxies, respectively (~\ref{fig: k96}).
    %I know it is exactly as Hossein's plot, but I can see any other choice to put here.

    The quiescent group of galaxies includes Elliptical (E), Bulge (B), S0, Sa, Sb, and Sc galaxies.
    Bulge groups represents galaxies similar to M31 and M81, which their UV and optical spectroscopy dominated by the stellar population in their bulges.
